---
title: "UNICEF Newborn Protocol Implementation Pilot Project \n Rapid Health Facilities Assessment (HFA) Report"
output:
  html_document:
    df_print: paged
params:
  hospital_name: "hospital name"
  pdf_document: default
  word_document: default
  always_allow_html: true
fontsize: 11pt
fonttype: Corbel
toc: yes

---

```{r, include=FALSE} 

knitr::opts_chunk$set(echo = FALSE,error = FALSE)

pacman::p_load(devtools, data.table, dplyr, forestmangr, ggplot2, lubridate, purrr, officer, here,
               reshape2, tibble, rvg, RedcapData, stringr, officer, flextable, rmarkdown, kableExtra, formattable)

```
# -------------------------------------------------------------------------------
``` {r, include=FALSE}

HFA_data <- fread(file=here::here("report","your data"))

data <- HFA_data %>% filter(hosp_id==params$hospital_name)

#date_of_visit <- data$date

```


**County**: `r data$county`

\newline
\newline
\newline

**Facility**: `r data$hosp_id`

\newline
\newline
\newline

\tableofcontents

\newline

*This Health Facility Readiness Assessment report is based on \n data collected on `r format(as.Date(data$date), '%d %B, %Y')`*

\newline

\newline

\newpage


## Table 1: Services offered at the facility, Staffing & Workload


``` {r, fig.align='left'}

table1 <- as.data.frame(data %>%
  dplyr::mutate('Maternal & Child Health (MCH)' = services___1,
                'Family Planning (FP)' = services___2,
                'Antenal Care (ANC)' = services___3,
                'Postnatal Care' = services___4,
                'Maternity/Delivery Services' = services___5,
                'HIV Care' = services___6,
                'Outpatient Services' = services___7,
                'Inpatient Services' = services___8,
                'Other Services' = other_services,
                'Has Labor Ward' = labor_ward)  %>% dplyr::mutate(
               'No. of Deliveries' = no_deliveries, 
               'No. of Live Births' = no_livebirths,
               'No. of Preterm Deliveries' = no_preterms,
               'No. of LBW Deliveries' = lbw_deliveries,
               'No. given CHX at birth' = no_chlorhex_digluc) %>% dplyr::mutate(
              'No. of Medical Officers' = docs,
              'No. of Clinical Officers' = cos,
              'No. of Nurses' = nurses,
              'No. of Nutritionists' = nutritionists) %>% select(
        'Maternal & Child Health (MCH)',
        'Family Planning (FP)',
        'Antenal Care (ANC)',
        'Postnatal Care',
        'Maternity/Delivery Services',
        'HIV Care',
        'Outpatient Services',
        'Inpatient Services',
        'Other Services',
        'Has Labor Ward',
        'No. of Deliveries',
        'No. of Live Births',
        'No. of Preterm Deliveries',
        'No. of LBW Deliveries',
        'No. given CHX at birth',
        'No. of Medical Officers',
        'No. of Clinical Officers',
        'No. of Nurses',
        'No. of Nutritionists') %>% t())


colnames(table1) <- NULL
colnames(table1) <- c("Offered")

table1 <- tibble::rownames_to_column(table1, "Service")

a <- table1[1:10, ]

b <- table1[11:15, ]
colnames(b) <- c("Workload", "Count")
rownames(b) <- c(1:5)
b_df <- data.frame(matrix(ncol = 2, nrow = 5))
colnames(b_df) <-  c("Workload", "Count")
b <- rbind(b, b_df)

c <- table1[16:19, ]
colnames(c) <- c("Carder", "Number")
rownames(c) <- c(1:4)
c_df <- data.frame(matrix(ncol = 2, nrow = 6))
colnames(c_df) <-  c("Carder", "Number")
c <- rbind(c, c_df)


services <- cbind(a, b, c)

services[is.na(services)] <- ""

services$Number <- as.numeric(as.character(services$Number))
services$Count <- as.numeric(as.character(services$Count))

#services <- regulartable(services) %>% bold(part = "header") %>% fontsize(part = "header", size = 10) 

#services %>% theme_zebra() %>% width(width = 1) %>% height_all(height = 0.2, part = "all") %>% fontsize(size = 10)
set_flextable_defaults(big.mark = " ", 
  font.size = 10, theme_fun = theme_vanilla,
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
 # background.color = "#EFEFEF",
  line_spacing = 0.8,
  table.layout = "autofit",
  cs.family	= "Corbel")

myft = flextable(services)
myft = align(myft, i = NULL, j = c(2, 4, 6), align = "center", part = "header")


myft = bg(myft, i = ~ Offered  == "Yes",
            j = 2,
            bg = "green")

myft = bg(myft, i = ~ Offered  == "No",
            j = 2,
            bg = "red")

myft = bg(myft, i = ~ Count <1,
            j = 4,
            bg = "red")

myft = bg(myft, i = ~ Number <1,
            j = 6,
            bg = "red")

add_footer(myft, values = "Services offered at the facility, Staffing & Workload") 
 

# 
# library(DT)
# datatable(services, 
#           options = list(
#             columnDefs = list(list(className = 'dt-center', targets = c(2,4, 6))))) %>% formatStyle('Offered',
#   backgroundColor = styleEqual(c("Yes", "No"), c('green', 'red'))) %>% 
#   formatStyle("Number", backgroundColor = styleEqual(c(0, 1), c('red', 'green')))
# 
# pacman::p_load(reactable)
# 
# 
#       ##########################
#       ### This section changed
#       ##########################
#     
#     # This part allows us to apply specific things to each column
# reactable(services, columns = list(
#   Offered = colDef(style = function(Offered) {
#     if (Offered =="Yes") {
#       color <- "green"
#     } else if (Offered == "No") {
#       color <- "red"
#     } else {
#       color <- "#777"
#     }
#     list(background = color, fontWeight = "bold")
#   })))



```

\newline

## Table 2: Availability of guidelines and job aides


```{r, fig.align='left'}

table2 <- as.data.frame(data %>% dplyr::mutate(
                           'IMNCI' = imnci_available,
                           'Basic Pediatric Protocols (BPP)' = bpp,
                           'Newborn Protocols' = newborn_protocols,
                           'MCH Booklets' = mch_booklet,
                           'Newborn resuscitation' = newborn_resusci,
                           'Birth & cord cutting' = birth_cord_cutting,
                           'Breastfeeding' = breastfeeding,
                           'Hypoglycaemia' = hypoglycaemia,
                           'Neonatal seizures' = neo_seizures,
                           'Assessing PSBI' = assess_psbi,
                           'Chlorhexidine' = chx,
                           'Kangaroo Mother Care' = k_mother_care,
                           'Handwashing' = handwashing,
                           'Warm Chain' = warm_chain,
                           'Immediate Newborn Care' = immediate_newb_care,
                           'Newborn Assessment' = assessment_newborn)  %>% select(
         'IMNCI',
         'Basic Pediatric Protocols (BPP)',
         'Newborn Protocols',
         'MCH Booklets',
         'Newborn resuscitation',
         'Birth & cord cutting',
         'Breastfeeding',
         'Hypoglycaemia',
         'Neonatal seizures',
         'Assessing PSBI',
         'Chlorhexidine',
         'Kangaroo Mother Care',
         'Handwashing',
         'Warm Chain',
         'Immediate Newborn Care',
         'Newborn Assessment') %>% t())

colnames(table2) <- NULL
colnames(table2) <- c("Availability")

table2 <- tibble::rownames_to_column(table2, "Guideline | Job Aide")

a <- table2[1:8, ]
b <- table2[9:16, ]

colnames(b) <- c("Guideline | Job Aide", "Availability")
rownames(b) <- c(1:8)

guidelines_job_aides <- cbind(a, b)

set_flextable_defaults(big.mark = " ", 
  font.size = 10, theme_fun = theme_vanilla,
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
#  background.color = "#EFEFEF",
  line_spacing = 0.8,
  table.layout = "autofit",
  cs.family	= "Corbel")

col_Names <- names(guidelines_job_aides)
nb_Col_Names <- length(col_Names)

for(i in 1 : nb_Col_Names)
{
  col_Names[i] <- paste0(col_Names[i], paste0(rep("\r", i), collapse = ""), collapse = "")
}

colnames(guidelines_job_aides) <- col_Names

#flextable(guidelines_job_aides)

#colnames(guidelines_job_aides)

# datatable(guidelines_job_aides, 
#           options = list(
#             columnDefs = list(list(className = 'dt-center', targets = c(2, 4, 6))))) %>% formatStyle(c("Availability\r\r", "Availability\r\r\r\r"),
#   backgroundColor = styleEqual(c("Yes", "No"), c('green', 'red')))

myft = flextable(guidelines_job_aides)
myft = align(myft, i = NULL, j = c(2, 4), align = "center", part = "header")

#colnames(guidelines_job_aides)

myft = bg(myft, i = ~ `Availability\r\r`  == "Yes",
            j = 2, bg = "green")

myft = bg(myft, i = ~ `Availability\r\r`  == "No",
            j = 2,  bg = "red")

myft = bg(myft, i = ~ `Availability\r\r\r\r`  == "Yes",
            j = 4, bg = "green")

myft = bg(myft, i = ~ `Availability\r\r\r\r`  == "No",
            j = 4,  bg = "red")

add_footer(myft, values = "Availability of guidelines and job aides") 


```

\newline

## Table 3: Organization of Neonatal Care


```{r, fig.align='left'}
table3 <- as.data.frame(data  %>% dplyr::mutate(
                              'Baby unique IP' = unique_id_ip,
                              'Baby independent medical record/file' = newborns_med_record,
                              'Where newborns are cared from:' = "",
                              'Postnatal ward' = where_newborn_cared___1,
                              'Pediatric ward' = where_newborn_cared___2,
                              'Separate ward/Nursery/NBU' = where_newborn_cared___3,
                              'Space within Maternity' = where_newborn_cared___4,
                              'No. of cots' = no_nbu_cots,
                              'No. of incubators' = nbu_num_incubators,
                              'Able to keep babies warm' = all_kept_warm,
                              'Heat source' = heat_source,
                              'Ward/Room heat source:' = "",
                              'Radian warmer' = room_heat_source___1,
                              'Resuscitaire' = room_heat_source___2,
                              'Other' = room_heat_source___3,
                              'Resuscitation checklist available' = checklist_resus_equip,
                              'Wall clock' = wall_clock,
                              'KMC practiced' = kmc,
                              'Immediate S-S initiated after birth' = skin_skin_care,
                              'Receive referrals' = receive_referrals,
                              'Weight limit for outborns' = outborn_wt_limit,
                              'Age limit for outborns' = outborn_age_limit,
                              'Outborns isolated in ward' = outborn_isolated,
                              'Weight limit for inborns' = inborn_wt_limit)  %>% 
                        select(
                          'Baby unique IP',
                          'Baby independent medical record/file',
                          'Where newborns are cared from:',
                          'Postnatal ward',
                          'Pediatric ward',
                          'Separate ward/Nursery/NBU',
                          'Space within Maternity',
                          'No. of cots',
                          'No. of incubators',
                          'Able to keep babies warm',
                          'Heat source',
                          'Ward/Room heat source:',
                          'Radian warmer',
                          'Resuscitaire',
                          'Other',
                          'Resuscitation checklist available',
                          'Wall clock',
                          'KMC practiced',
                          'Immediate S-S initiated after birth',
                          'Receive referrals',
                          'Weight limit for outborns',
                          'Age limit for outborns',
                          'Outborns isolated in ward',
                          'Weight limit for inborns') %>% t())

colnames(table3) <- NULL
colnames(table3) <- c("Response")

table3 <- tibble::rownames_to_column(table3, "Indicator")

a <- table3[1:12, ]
b <- table3[13:24, ]

colnames(b) <- c("Indicator", "Response")
rownames(b) <- c(1:12)

care_organization <- cbind(a, b)


set_flextable_defaults(big.mark = " ", 
  font.size = 10, theme_fun = theme_vanilla,
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
#  background.color = "#EFEFEF",
  line_spacing = 0.8,
  table.layout = "autofit",
  cs.family	= "Corbel")

col_Names <- names(care_organization)
nb_Col_Names <- length(col_Names)

for(i in 1 : nb_Col_Names)
{
  col_Names[i] <- paste0(col_Names[i], paste0(rep("\r", i), collapse = ""), collapse = "")
}

colnames(care_organization) <- col_Names

#flextable(care_organization)

# colnames(care_organization)
# 
# datatable(care_organization, 
#           options = list(
#             columnDefs = list(list(className = 'dt-center', targets = c(2,4))))) %>% formatStyle(c("Response\r\r", "Response\r\r\r\r"),
#   backgroundColor = styleEqual(c("Yes", "No"), c('green', 'red')))


myft = flextable(care_organization)
myft = align(myft, i = NULL, j = c(2, 4), align = "center", part = "header")

#colnames(guidelines_job_aides)

myft = bg(myft, i = ~ `Response\r\r`  == "Yes",
            j = 2, bg = "green")

myft = bg(myft, i = ~ `Response\r\r`  == "No",
            j = 2,  bg = "red")

myft = bg(myft, i = ~ `Response\r\r` =="0",
            j = 2,  bg = "red")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "Yes",
            j = 4, bg = "green")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "No",
            j = 4,  bg = "red")

add_footer(myft, values = "Organization of Neonatal Care") 


```

\newline

## Table 4: Availability of Drugs, fluids and Feeds


```{r, fig.align='left'}

table4 <- as.data.frame(data  %>% dplyr::mutate(
  '1% TEO' = teo_one_perc,
  '7.1% Chlorhexidine gel' = chx_gel,
  'Vitamin K' = vit_k,
  'Benzyl Penicillin' = xpen,
  'Gentamicin' = genta,
  'Oral Amoxicillin' = oral_amox,
  'Phenobarbitone (injection)' = phenobarb_inj,
  'Adrenaline' = adrenlne,
  'Phenytoin IV' = phenytoin_iv,
  'Oral diclofenac' = oral_diclofenac,
  'Paracetamol' = paracetamol,
  'Glucose 10%' = glucose_10perc,
  'Normal saline IV' = normal_saline_iv,
  'Thermometer (digital/clinical/thermo-gun)' = thermometer,
  'Wall thermometer' = wall_thermometer,
  'Infant/Baby weighing scales' = weighing_scale,
  'Measuring tape' = measuring_tape,
  'Pulse oximeter' = pulse_oxim,
  'No. of Pulse Oximeters' = pulse_oxs,
  'Resuscitaire' = resuscitaire,
  'No. of Oxygen Cylinders' = ox_cylinders,
  'Suction devices available' = suc_devices)  %>% 
    select(
      '1% TEO',
      '7.1% Chlorhexidine gel',
      'Vitamin K',
      'Benzyl Penicillin',
      'Gentamicin',
      'Oral Amoxicillin',
      'Phenobarbitone (injection)',
      'Adrenaline',
      'Phenytoin IV',
      'Oral diclofenac',
      'Paracetamol',
      'Glucose 10%',
      'Normal saline IV',
      'Thermometer (digital/clinical/thermo-gun)',
      'Wall thermometer',
      'Infant/Baby weighing scales',
      'Measuring tape',
      'Pulse oximeter',
      'No. of Pulse Oximeters',
      'Resuscitaire',
      'No. of Oxygen Cylinders',
      'Suction devices available') %>% t())


colnames(table4) <- NULL
colnames(table4) <- c("Response")

table4 <- tibble::rownames_to_column(table4, "Indicator")

a <- table4[1:11, ]
b <- table4[12:22, ]

colnames(b) <- c("Indicator", "Response")
rownames(b) <- c(1:11)

drugs_fluids_equipments <- cbind(a, b)

set_flextable_defaults(big.mark = " ", 
  font.size = 10, theme_fun = theme_vanilla,
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
#  background.color = "#EFEFEF",
  line_spacing = 0.8,
  table.layout = "autofit",
  cs.family	= "Corbel")

col_Names <- names(drugs_fluids_equipments)
nb_Col_Names <- length(col_Names)

for(i in 1 : nb_Col_Names)
{
  col_Names[i] <- paste0(col_Names[i], paste0(rep("\r", i), collapse = ""), collapse = "")
}

colnames(drugs_fluids_equipments) <- col_Names

#flextable(drugs_fluids_equipments)

# colnames(drugs_fluids_equipments)
# 
# datatable(drugs_fluids_equipments, 
#           options = list(
#             columnDefs = list(list(className = 'dt-center', targets = c(2,4))))) %>% formatStyle(c("Response\r\r", "Response\r\r\r\r"),
#   backgroundColor = styleEqual(c("Yes", "No"), c('green', 'red')))

myft = flextable(drugs_fluids_equipments)
myft = align(myft, i = NULL, j = c(2, 4), align = "center", part = "header")

#colnames(guidelines_job_aides)

myft = bg(myft, i = ~ `Response\r\r`  == "Yes",
            j = 2, bg = "green")

myft = bg(myft, i = ~ `Response\r\r`  == "No",
            j = 2,  bg = "red")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "Yes",
            j = 4, bg = "green")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "No",
            j = 4,  bg = "red")

myft = bg(myft, i = ~ `Response\r\r\r\r` =="0",
            j = 4,  bg = "red")

add_footer(myft, values = "Availability of Drugs, fluids and Feeds") 


```

\newline

## Table 5: Infection Prevention & Control (IPC) & Personal Protective Equipment (PPEs)


```{r, fig.align='left'}

table5 <- as.data.frame(data %>% dplyr::mutate(
                              'Running water & soap at delivery area' = water_soap,
                              'Alcohol based sanitizer' = alco_sanitizer,
                              'Handwashing observed' = ipc_handwashing,
                              'Examination gloves' = gloves_exam,
                              'Health worker masks' = masks_hcws,
                              'Alcohol based hand rub' = alcohol_handrub,
                              'Bio-hazardous bag' = biohazardous_bag,
                              'Safety box' = safetybox,
                              'Soap' = soap,
                              'Chlorine' = chlorine) %>% select(
                      'Running water & soap at delivery area',
                      'Alcohol based sanitizer',
                      'Handwashing observed',
                      'Examination gloves',
                      'Health worker masks',
                      'Alcohol based hand rub',
                      'Bio-hazardous bag',
                      'Safety box',
                      'Soap',
                      'Chlorine') %>% t())


colnames(table5) <- NULL
colnames(table5) <- c("Response")

table5 <- tibble::rownames_to_column(table5, "Indicator")

a <- table5[1:5, ]
b <- table5[6:10, ]

colnames(b) <- c("Indicator", "Response")
rownames(b) <- c(1:5)

ipc_ppes <- cbind(a, b)

set_flextable_defaults(big.mark = " ", 
  font.size = 10, theme_fun = theme_vanilla,
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
#  background.color = "#EFEFEF",
  line_spacing = 0.8,
  table.layout = "autofit",
  cs.family	= "Corbel")

col_Names <- names(ipc_ppes)
nb_Col_Names <- length(col_Names)

for(i in 1 : nb_Col_Names)
{
  col_Names[i] <- paste0(col_Names[i], paste0(rep("\r", i), collapse = ""), collapse = "")
}

colnames(ipc_ppes) <- col_Names

#flextable(ipc_ppes)

# colnames(ipc_ppes)
# 
# datatable(ipc_ppes, 
#           options = list(
#             columnDefs = list(list(className = 'dt-center', targets = c(2,4))))) %>% formatStyle(c("Response\r\r", "Response\r\r\r\r"),
#   backgroundColor = styleEqual(c("Yes", "No"), c('green', 'red')))


myft = flextable(ipc_ppes)
myft = align(myft, i = NULL, j = c(2, 4), align = "center", part = "header")

#colnames(guidelines_job_aides)

myft = bg(myft, i = ~ `Response\r\r`  == "Yes",
            j = 2, bg = "green")

myft = bg(myft, i = ~ `Response\r\r`  == "No",
            j = 2,  bg = "red")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "Yes",
            j = 4, bg = "green")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "No",
            j = 4,  bg = "red")

add_footer(myft, values = "Infection Prevention & Control (IPC) & Personal Protective Equipment (PPEs)") 


```

\newline

## Table 6: Monitoring & Evaluation (Information Systems) & Referral Systems

```{r, fig.align='left'}

table6 <- as.data.frame(data  %>% dplyr::mutate(
                                'Receive referrals' = receive_referrals,
                                'Referral system in place' = referral_sys,
                                'Referral/transport means:' = "",
                                'Facility ambulance' = referral_means___1,
                                'Sub-county ambulance' = referral_means___2,
                                'Patient own transport' = referral_means___3,
                                'Other means' = referral_means___4,
                                'Facility phone' = facility_phone,
                                'Referral form' = referral_form,
                                'Community Referral Form (MoH 100)' = moh100_available,
                                'Maternity register (MOH 333)' = mat_register,
                                'Inpatient neonatal register (MOH373)' = inpatient_nn_register,
                                'Under five register (MOH 204A)' = under_five_reg,
                                'Newborn Admission Record Forms (NAR)' = nar,
                                'Referral forms' = referral_forms,
                                'Mother & Child Health Handbook (MOH 216)' = mch_handbook,
                                'Birth notification forms' = birth_forms,
                                'Vitals monitoring chart' = vitals_chart) %>% select(
    'Receive referrals',
    'Referral system in place',
    'Referral/transport means:',
    'Facility ambulance',
    'Sub-county ambulance',
    'Patient own transport',
    'Other means',
    'Facility phone',
    'Referral form',
    'Community Referral Form (MoH 100)',
    'Maternity register (MOH 333)',
    'Inpatient neonatal register (MOH373)',
    'Under five register (MOH 204A)',
    'Newborn Admission Record Forms (NAR)',
    'Referral forms' = referral_forms,
    'Mother & Child Health Handbook (MOH 216)',
    'Birth notification forms',
    'Vitals monitoring chart') %>% t())


colnames(table6) <- NULL
colnames(table6) <- c("Response")

table6 <- tibble::rownames_to_column(table6, "Indicator")

a <- table6[1:9, ]
b <- table6[10:18, ]

colnames(b) <- c("Indicator", "Response")
rownames(b) <- c(1:9)

referral_m_e <- cbind(a, b)

set_flextable_defaults(big.mark = " ", 
  font.size = 10, theme_fun = theme_vanilla,
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
#  background.color = "#EFEFEF",
  line_spacing = 0.8,
  table.layout = "autofit",
  cs.family	= "Corbel")

col_Names <- names(referral_m_e)
nb_Col_Names <- length(col_Names)

for(i in 1 : nb_Col_Names)
{
  col_Names[i] <- paste0(col_Names[i], paste0(rep("\r", i), collapse = ""), collapse = "")
}

colnames(referral_m_e) <- col_Names

#flextable(referral_m_e)

# colnames(referral_m_e)
# 
# datatable(referral_m_e, 
#           options = list(
#             columnDefs = list(list(className = 'dt-center', targets = c(2,4))))) %>% formatStyle(c("Response\r\r", "Response\r\r\r\r"),
#   backgroundColor = styleEqual(c("Yes", "No"), c('green', 'red')))



myft = flextable(referral_m_e)
myft = align(myft, i = NULL, j = c(2, 4), align = "center", part = "header")

#colnames(guidelines_job_aides)

myft = bg(myft, i = ~ `Response\r\r`  == "Yes",
            j = 2, bg = "green")

myft = bg(myft, i = ~ `Response\r\r`  == "No",
            j = 2,  bg = "red")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "Yes",
            j = 4, bg = "green")

myft = bg(myft, i = ~ `Response\r\r\r\r`  == "No",
            j = 4,  bg = "red")

add_footer(myft, values = "Monitoring & Evaluation (Information Systems) & Referral Systems") 


```


